Commutative Character Sheaves

### 2015-09-28 followup.tex
Out of time for today  . .  .

\begin{theorem}\label{thm:Gab}
Pull-back along the abelianization $q : G \to G\ab$
\[
q^* : \CCS(G\ab) \to \CCS(G)
\]
is an equivalence of categories.
\end{theorem}

@@

\begin{lemma}\label{lem:equivariant}
$\CCS(G)$ and $\CCS_G(G)$ are equivalent.
\end{lemma}
%\begin{proposition}
%Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$. Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative. 
%\end{proposition}

@@

\begin{remark}
Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$.
\end{remark}

>>>>

\begin{theorem}\label{thm:Gab}
Under these hypotheses, pull-back along the abelianization $q : G \to G\ab$
\[
q^* : \CCS(G\ab) \to \CCS(G)
\]
is an equivalence of categories.
\end{theorem}

@@

\begin{lemma}\label{lem:equivariant}
$\CCS(G)$ and $\CCS_G(G)$ are equivalent.
[Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$; conversely, if a linear character sheaf on $G$ is equivariant for conjugation, then it is commutative?]
\end{lemma}

@@

\begin{remark}
Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$. [Is this correct?]
\end{remark}
